ACNP 2024 MS ANXIETY

### 2024-08-30 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL.Rmd
added. new plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(stringr)
library(MatchIt)
library(ggpubr)
library(tidymv)

#functions
source("~/BBL/msanxiety/scripts/ms_functions.R")
```

@@

#### Plot promis x anxiety dose, group by mental vs physical health
```{r plot_Promis_x_anxiety}
#set mood versus physical domains
mood_domains <- c("Mental_Health_and_Mood",
                "Social_Activities_Satisfaction",
                "Carrying_Out_Social_Activities",
                "Emotional_Problems", 
                "Quality_of_Life",
                "PostOp.PROMIS.Mental.Score")

@@

# Reshape the data from wide to long format
df_for_promis_plot_mental_vs_physical_healthy <- df_people_with_promis_data_scores_added_unique %>%
  group_by(EMPI) %>%
  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
  dplyr::select(EMPI,
                anxiety_dose,
                physical_health_score,
                mental_health_score) %>%
  gather(health_variable, PROMIS_Score, -anxiety_dose, -EMPI) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  group_by(anxiety_dose, health_variable) %>%
  summarise(mean_promis_score = mean(PROMIS_Score , na.rm = TRUE),
            sd_promis_score = sd(PROMIS_Score, na.rm = TRUE),
            sem_promis_score = sd(PROMIS_Score, na.rm = TRUE) / sqrt(n())) %>%
  ungroup()

custom_colors <- c("physical_health_score" = "#9ACD32","mental_health_score" =  "#4B0082")

custom_colors_simple <- c("#9ACD32", "#4B0082") #done in alphabetical order.

# Create the ggplot
promis_with_post_op_mental_vs_physical <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, color = health_variable)) +
  geom_line(size = 1.2) +
  scale_x_continuous(breaks = c(0, 1, 2)) +
  scale_y_continuous(limits = c(0, 7)) +
  geom_errorbar(aes(ymin = mean_promis_score - sem_promis_score, ymax = mean_promis_score + sem_promis_score), width = 0.2, size = 0.8)  +
  theme(
       # plot.title = element_text(size=16, hjust = 0.55),
      #  axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
      #  axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
      #  legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white")) +
  labs(x = "Anxiety Dose", y = "Mean PROMIS Score", 
       title = "PROMIS Scores by Anxiety Dose") +
#  scale_color_brewer(palette = "Set3") 
  scale_color_manual(values = custom_colors_simple)
promis_with_post_op_mental_vs_physical

# Create the ggplot -> bar
promis_with_post_op_mental_vs_physical_bar <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, fill = health_variable)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +  
  geom_errorbar(aes(ymin = mean_promis_score - sem_promis_score, ymax = mean_promis_score + sem_promis_score), 
                width = 0.2, size = 0.8, color = "black", position = position_dodge(width = 0.9)) +
  scale_x_continuous(breaks = c(0, 1, 2)) +
  scale_y_continuous(limits = c(0, 7)) +
  theme_minimal() +
  labs(x = "Anxiety Dose", y = "Mean PROMIS Score", 
       title = "PROMIS Scores by Anxiety Dose") +
  scale_fill_manual(values = custom_colors)

promis_with_post_op_mental_vs_physical_bar

@@

####Test promis*anxiety dose  stats
#####Physical and Mental Health together
```{r phsy_and_mental_step_x_anxiety_dose}
###
df_for_promis_plot_mental_vs_physical_healthy_test <- df_people_with_promis_data_scores_added_unique %>%
  group_by(EMPI) %>%
  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
  mutate(phys_mental_diff_score = physical_health_score-mental_health_score) %>%
  dplyr::select(EMPI,
                anxiety_dose,
                physical_health_score,
                mental_health_score,
                phys_mental_diff_score)

#anxiety_dose  -0.7345     0.2946  -2.493   0.0153 * 
anxiety_dose_x_phys_score <- lm(physical_health_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
summary(anxiety_dose_x_phys_score)

#anxiety_dose  -1.1181     0.2681  -4.171 9.59e-05 ***
anxiety_dose_x_mental_score <- lm(mental_health_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
summary(anxiety_dose_x_mental_score)

#anxiety_dose   0.3836     0.2391   1.605    0.114
anxiety_dose_x_diff_score <- lm(phys_mental_diff_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
summary(anxiety_dose_x_diff_score)

#looking at anxiety_dose = 2 only, 0.22 -> sample size too small

mental_vs_physical_health_t <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
mental_vs_physical_health_t

#looking at physical health and mental health in sick vs healthy

#physical health, sick vs healthy - t = 2.0048, df = 8.6555, p-value = 0.07722
physical_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
physical_health_t_sick_vs_healthy

#mental health, sick vs healthy - t = 3.6838, df = 8.1324, p-value = 0.006011
mental_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
mental_health_t_sick_vs_healthy
```

@@

#### Uncinate by Anxiety Dose (vol and prop)
```{r uncinateByAnxietyDose}

@@

#### Plots Uncinate R,L,mean Prop
```{r plots_uncinate}
  #proportion injured over R Uncinate prop
  # Of note, PROP AND VOL ARE LINEARLY RELATED -> USE PROP FOR ANALYSIS OTHERWISE THE GRAPHS BECOME CONFUSING TO LOOK AT. PROP is proportion of total fascicle injury

#n=371
df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1)

prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_R_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot

 #proportion injured over R Uncinate prop - geom_bar
means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))

df_UF_R_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))

names(df_UF_R_mean_by_anxiety_dose) <- c("mean_UF_R", "Anxiety_dose")

df_UF_R_mean_by_anxiety_dose <- df_UF_R_mean_by_anxiety_dose %>%
  mutate(mean_UF_R = as.numeric(mean_UF_R)) %>%
  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))

prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_UF_R_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_R, fill=Anxiety_dose)) +
  geom_bar(stat="identity") +  
  ylim(0,0.5)+
#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
        panel.background = element_rect(colour = "white", fill = "white"))
prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot_bar

  #proportion injured over L Uncinate prop
prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_L_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot

 #proportion injured over L Uncinate prop - geom_bar
means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))

df_UF_L_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))

names(df_UF_L_mean_by_anxiety_dose) <- c("mean_UF_L", "Anxiety_dose")

df_UF_L_mean_by_anxiety_dose <- df_UF_L_mean_by_anxiety_dose %>%
  mutate(mean_UF_L = as.numeric(mean_UF_L)) %>%
  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))

prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_UF_L_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_L, fill=Anxiety_dose)) +
  geom_bar(stat="identity") +  
  ylim(0,0.5)+
#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
        panel.background = element_rect(colour = "white", fill = "white"))
prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot_bar

#mean UF

  #proportion injured over mean Uncinate prop
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=mean_UF_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot

 #proportion injured over mean Uncinate prop - geom_bar
means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$mean_UF_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$mean_UF_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$mean_UF_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))

df_mean_UF_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))

names(df_mean_UF_mean_by_anxiety_dose) <- c("mean_UF_mean", "Anxiety_dose")

df_mean_UF_mean_by_anxiety_dose <- df_mean_UF_mean_by_anxiety_dose %>%
  mutate(mean_UF_mean = as.numeric(mean_UF_mean)) %>%
  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))

prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_mean_UF_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_mean, fill=Anxiety_dose)) +
  geom_bar(stat="identity") +  
  ylim(0,0.5)+
#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
        panel.background = element_rect(colour = "white", fill = "white"))
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(stringr)
library(MatchIt)
library(ggpubr)
library(tidymv)
library(viridis)  # Ensure you have the viridis package
#functions
source("~/BBL/msanxiety/scripts/ms_functions.R")
```

@@

#### Plot 
#####Promis x anxiety dose, group by mental vs physical health
```{r plot_Promis_x_anxiety}
#set mood versus physical domains
mood_domains <- c("Mental_Health_and_Mood",
                "Social_Activities_Satisfaction",
                "Carrying_Out_Social_Activities",
                "Emotional_Problems", 
                "Quality_of_Life",
                "PostOp.PROMIS.Mental.Score")

@@

# Reshape the data from wide to long format
df_for_promis_plot_mental_vs_physical_healthy <- df_people_with_promis_data_scores_added_unique %>%
  group_by(EMPI) %>%
  mutate("Physical Health Burden" = sum(across(physical_domains))/length(physical_domains)) %>%
  mutate("Mental Health Burden" = sum(across(mood_domains))/length(mood_domains)) %>%
  dplyr::select(EMPI,
                anxiety_dose,
                "Physical Health Burden",
                "Mental Health Burden") %>%
  gather(health_variable, PROMIS_Score, -anxiety_dose, -EMPI) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  group_by(anxiety_dose, health_variable) %>%
  summarise(mean_promis_score = mean(PROMIS_Score , na.rm = TRUE),
            sd_promis_score = sd(PROMIS_Score, na.rm = TRUE),
            sem_promis_score = sd(PROMIS_Score, na.rm = TRUE) / sqrt(n())) %>%
  ungroup()

#custom_colors_simple <- c("#9ACD32", "#4B0082") #done in alphabetical order.

# Define the desired order of legend items
desired_order <- c("Physical Health Burden", "Mental Health Burden")

# Ensure the factor levels are set to match the desired order
df_for_promis_plot_mental_vs_physical_healthy$health_variable <- factor(
  df_for_promis_plot_mental_vs_physical_healthy$health_variable,
  levels = desired_order
)

# Define custom colors, ensuring the names match the levels of the factor
custom_colors_simple <- c("Physical Health Burden" = "#4B0082",  # Purple
                          "Mental Health Burden" = "#9ACD32")  # Green

# Create the ggplot
promis_with_post_op_mental_vs_physical <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, color = health_variable)) +
  geom_line(size = 1.2) +
  scale_x_continuous(breaks = c(0, 1, 2),  # Keep numeric values on x-axis
                     labels = c("MS+noA", "MS+mildA", "MS+severeA")) +  # Set custom labels for each numeric value
  scale_y_continuous(limits = c(0, 7)) +
  geom_errorbar(aes(ymin = mean_promis_score - sem_promis_score, ymax = mean_promis_score + sem_promis_score), width = 0.2, size = 0.8)  +
  theme(
        axis.text.y = element_text(size=12, colour = "black"),
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size=12, colour = "black"),
        legend.title = element_blank(),
        legend.position = c(0.8, 0.95),  # Move legend to upper right of plot area (0.9, 0.9 corresponds to top-right)
        legend.background = element_rect(fill = "white"),  # Set legend background to white
        legend.key = element_rect(fill = "white", color = "white"),  # Set legend key background to white
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white")) +
  labs(y= "Mean PROMIS Score") +
  scale_color_manual(values = custom_colors_simple, breaks = desired_order)

promis_with_post_op_mental_vs_physical
#save pdf
pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/promis_with_post_op_mental_vs_physical.pdf"))
  promis_with_post_op_mental_vs_physical
dev.off()

@@

@@

#### Uncinate by Anxiety Dose 
```{r uncinateByAnxietyDose}

@@

#### Plots 
#####Uncinate R,L,mean Prop
```{r plots_uncinate}
  #proportion injured over R Uncinate prop

#n=372
df_mean_UF_mean_by_anxiety_severity <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1) %>%
  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
  mutate(mean_UF_prop = mean_UF_prop*100) %>%
  group_by(anxiety_severity) %>%
  summarise(mean_UF_mean = round(mean(mean_UF_prop , na.rm = TRUE),0),
            sd_UF = sd(mean_UF_prop, na.rm = TRUE),
            sem_UF = sd(mean_UF_prop, na.rm = TRUE) / sqrt(n())) %>%
  mutate(anxiety_severity = factor(anxiety_severity, levels = unique(anxiety_severity))) %>%
  ungroup()

prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_mean_UF_mean_by_anxiety_severity, aes(x=anxiety_severity, y=mean_UF_mean, fill=anxiety_severity)) +
  geom_bar(stat="identity", width = .6) +  
  geom_errorbar(aes(ymin = mean_UF_mean - sem_UF, ymax = mean_UF_mean + sem_UF), width = 0.2, size = 0.8)  +
  scale_fill_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
  ylim(0,45)+
  theme(axis.text.x = element_text(size=12, colour = "black"),
        axis.text.y = element_text(size=12, colour = "black"),
        axis.title.y = element_text(size=16, colour = "black"),
        axis.title.x = element_blank(),
        axis.line = element_line(linewidth = 1.5, colour="black"),
        legend.position = "none",
        panel.background = element_rect(colour = "white", fill = "white")) + 
  labs(y = "Percent (%) of Uncinate Injured")
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar

#save pdf
pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_bar.pdf"))
  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
dev.off()

```
##### Uncinate Violin Plot
```{r uncinate_violin}
#### trying prettier things
df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1) %>%
  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
  mutate(mean_UF_prop = mean_UF_prop*100)

# Create the plot with narrower violins and error bars
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, fill = anxiety_severity)) +
  geom_violin(width = 0.6, alpha =1.5, color = "black", trim = FALSE) +  # Adjust violin width and transparency
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  ylim(0,100) +
  #geom_errorbar(aes(ymin = mean_UF_prop - sem_UF_prop, ymax = mean_UF_prop + sem_UF_prop), width = 0.2, color = "black") +  # Add error bars
  scale_fill_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
  #theme_minimal(base_size = 14) +  # Use a minimal theme with a base font size
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),  # Rotate x-axis labels for better readability
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white"),
    plot.margin = margin(10, 10, 10, 10)  # Add margins around the plot
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot

#save pdf
pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_violin.pdf"))
  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
dev.off()

```
##### Geom point
```{r geom_point}
#### trying prettier things
df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1) %>%
  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
  mutate(mean_UF_prop = mean_UF_prop*100)

# Create the plot with narrower violins, viridis colors, and horizontal lines at means
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_point(position = position_jitter(.1), size = 2, alpha = 0.8) +  # Add points with jitter using viridis colors
  stat_summary(fun = "mean", geom = "crossbar", width = 0.3, color = "black", size = 0.5) +  # Add horizontal lines at means
  scale_color_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale for points
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),  # X-axis labels
    axis.text.y = element_text(size = 12, colour = "black"),  # Y-axis labels
    axis.title.y = element_text(size = 16, colour = "black"),  # Y-axis title
    axis.title.x = element_blank(),  # Remove X-axis title
    axis.line = element_line(linewidth = 1.5, colour = "black"),  # Axis lines
    legend.position = "none",  # Remove legend
    panel.background = element_rect(colour = "white", fill = "white")  # Background
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")  # Y-axis label

# Display the plot
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot

#save pdf
pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_dot.pdf"))
  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
dev.off()
